FoRTE baseline

### 2019-06-05 analysis/paper/paper.Rmd
Draft first two paragraphs of intro

>>>>

Temperate forests in the Upper Midwest are important.
{C sequestration}.
{Other ecosystem services}.
However, the fate of these forests is highly uncertain.
The natural ecological succession of these forests has been significantly altered by the interactions of a significantly different and rapidly changing climate, and novel disturbance regimes under which some natural disturbances (e.g. fire) are suppressed while others (e.g. harvest; pests and pathogens) may be becoming more frequent. <!-- TODO refs -->
Therefore, predictions about the future of these forests based on past analogs may not be reliable.

Instead, more reliable predictions can be obtained by using dynamic vegetation models that explicitly represent process involved in forest growth and mortality.
Vegetation models fall broadly along the following spectrum of complexity.
On one side are relatively simple "Big leaf" models---such as PNET, SiBCASA, and Biome-BGC <!-- TODO refs; more examples? -->---in which the vegetation at a particular location consists essentially of a single large "plant" whose characteristics are the (weighted) average of all the vegetation at that site. <!-- TODO refs -->
These models were designed originally to simulate the land surface boundary condition for atmospheric general circulation models, though similar models continue to be applied successfully to simulate biogeochemical processes in many ecosystem science contexts. <!-- TODO refs -->
On the other end of the spectrum are "individual-based" models (a.k.a. "gap models"), which explicitly simulate multiple indivduals competing for resources at a single site [@shugart_2015_computer]. <!-- TODO other refs? -->
Examples of such models are LANDIS <!-- TODO ref !--> and UVAFME. <!-- TODO ref --> <!-- TODO Others? -->
Because these models can explicitly represent inter-specific differences in plant productivity, resource allocation, and stress tolerance (among others), as well as the competition that emerges out of these differences, they may be better able to represent changes in ecosystem-scale processes, especially in no-analog conditions [@purves_2008_predictive].
Moreover, these models' predictions of species composition and ecosystem structure are relevant outside of carbon cycle science, particularly for forest management and wildlife conservation. <!-- TODO refs -->
However, these benefits of individual-based models come at the cost of much higher data and computational requirements, which effectively restrict their application to individual, well-studied sites. <!-- TODO refs. Also, is this actually true? -->
